\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2019-08-22 sections/results.tex
Add: Updates for draft v3

  % TODO: Update this table
  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Process} & \textbf{Tool} & \textbf{Parameters} \\
      \hline
      Denoising and Clustering & Dada2/Deblur & default \\
      Taxonomy Assignment & \ac{ncbi} with Blast & RefSeq database \\
      OTU Processing & Based on statistical power & Dynamic cutoff \\
      Network Inference & Consensus method & - \\
      \hline
    \end{tabular}
    \caption{Default tools and parameters for the pipeline}
    \label{tab:default_options}
  \end{table}

@@

  In order to analyze the effect of different statistical methods on the inferred co-occurrence networks, we generate co-occurrence networks using all possible combinations of methods and estimate the variability in the networks due to each choice.
  Figure \ref{fig:figure2} shows the fraction of total variation among the co-occurrence networks as contributed by each of the four main steps of the pipeline.
  The 16S reference database contributes to the most variation ($\sim25\%$) in the networks and the networks can be clearly separated based on the database used.
  \todo[size=\footnotesize]{Update with full results}
  This indicates that the taxonomy assigned to the reference sequences drastically alters the co-occurrence network and this change is much more significant than how the reference sequences themselves are identified (in the denoise/cluster step).
  The residual variation can be seen as an artifact that arises due to the effect on the resultant network when multiple steps are changed at the same time.
  Another interesting observation has been that the dissimilarity between the networks decreases when the low abundance OTUs are removed from the network.

@@

  Unlike in the previous sections, where were we evaluated the performance of methods on mock datasets, there are no such datasets that contain a set of known interactions for the evaluation of the network inference algorithms.
  Therefore, we propose the construction of a \hl{consensus network} (Figure~\ref{fig:figure5}C) involving \ac{magma}, \ac{mldm}, \ac{spieceasi} and \ac{sparcc} by merging the p-values generated from bootstraps of the original taxonomy composition table.
  The resulting network will have weights reported by all four methods.

@@

  \subsection*{The default network}

  The default tools and parameters chosen for the pipeline are given in Table~\ref{tab:default_options}.
  The default

>>>>

  % TODO: Update this table
  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Process} & \textbf{Tool} & \textbf{Parameters} \\
      \hline
      Denoising and Clustering & Dada2/Deblur & default \\
      Taxonomy Assignment & \ac{ncbi} with Blast & RefSeq database \\
      OTU Processing & Based on statistical power & Dynamic cutoff \\
      Network Inference & Consensus method & - \\
      \hline
    \end{tabular}
    \caption{Default tools and parameters for the pipeline. Detailed information can be found in the methods section}
    \label{tab:default_options}
  \end{table}

@@

  In order to analyze the effect of different statistical methods on the inferred co-occurrence networks, we generate co-occurrence networks using all possible combinations of methods and estimate the variability in the networks due to each choice.
  Figure \ref{fig:figure2} shows the fraction of total variation among the co-occurrence networks as contributed by each of the four main steps of the pipeline.
  The 16S reference database contributes to the most variation ($\sim25\%$) in the networks and the networks can be clearly separated based on the database used.
  \todo[size=\footnotesize]{Update with full results}
  This indicates that the taxonomy assigned to the reference sequences drastically alters the co-occurrence network and this change is much more significant than how the reference sequences themselves are identified (in the denoise/cluster step).
  We believe that this clustering is due to the mislabelling of constitutive taxa that are present in high abundance in the community.
  The residual variation can be seen as an artifact that arises due to the effect on the resultant network when multiple steps are changed at the same time.
  Another interesting observation has been that the dissimilarity between the networks decreases when the low abundance OTUs are removed from the network.
  These results enable us to believe that the most important criterion for accurate comparative analyses of co-occurrence networks is the taxonomy reference database.

@@

  Unlike in the previous sections, where were we evaluated the performance of methods on mock datasets, there are no such datasets that contain a set of known interactions for the evaluation of the network inference algorithms.
  Therefore, we propose the construction of a \hl{consensus network} (Figure~\ref{fig:figure5}C) involving \ac{magma}, \ac{mldm}, \ac{spieceasi} and \ac{sparcc} by merging the p-values generated from bootstraps of the original taxonomy composition table using the Browns pvalue combining method (ref).
  The resulting network will have weights reported by all four methods.

@@

  \subsubsection*{The default pipeline}

  The systematic analysis performed in the previous sections allows us to suggest the set of tools and parameters that produce more accurate and robust co-occurrence networks.
  These tools and parameters chosen as the defaults for the pipeline and are given in Table~\ref{tab:default_options}.
  The recommended tool for the \ac{dc} step are \ac{dada2} or Deblur were chosen based on their accuracy in recapitulating the reference sequences in mock communities and synthetic data.
  The choice of the taxonomy reference database in the \ac{ta} step is dictated largely by the species expected to be present in the sample as well the database used in similar studies if comparison is a goal.
  Nevertheless, we suggest \ac{ncbi} RefSeq along with blast+ as the query tool since the database is updated regularly and has a broad collection of taxonomies.
  The abundance threshold at the \ac{op} step is determined automatically based on the number of samples and the required statistical power.
  Finally, we use the Browns pvalue combining method on the networks generated using \ac{magma}, \ac{mldm}, \ac{spieceasi} and \ac{sparcc} to obtain a final consensus network in the \ac{ni} step.
